A publishing infrastructure for AI-assisted academic authoring

### 2023-12-26 latex/manuscript.tex
latex: add authors highest degree
latex: add structure of disclosure statements
latex: add funding statement

\begin{itemize}
\item
  \textbf{Milton Pividori}
  \includesvg[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-3035-4403}{0000-0002-3035-4403}
  · \includesvg[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/miltondp}{miltondp}
  · \includesvg[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/miltondp}{miltondp}
  · \includesvg[width=0.16667in,height=0.16667in]{images/mastodon.svg}
  \href{https://genomic.social/@miltondp}{@miltondp@genomic.social} \\
  Department of Biomedical Informatics, University of Colorado School of Medicine, Aurora, CO 80045, USA; Department of Genetics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA
  · Funded by The National Human Genome Research Institute, K99/R00 HG011898; The Alfred P. Sloan Foundation, G-2023-20989; The Eunice Kennedy Shriver National Institute of Child Health and Human Development, R01 HD109765
\item
  \textbf{Casey S. Greene}
  \textsuperscript{\protect\hyperlink{correspondence}{\Letter}}
  \includesvg[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0001-8713-9213}{0000-0001-8713-9213}
  · \includesvg[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/cgreene}{cgreene}
  · \includesvg[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/GreeneScientist}{GreeneScientist}
  · \includesvg[width=0.16667in,height=0.16667in]{images/mastodon.svg}
  \href{https://genomic.social/@greenescientist}{@greenescientist@genomic.social} \\
  Center for Health AI, University of Colorado School of Medicine, Aurora, CO 80045, USA; Department of Biomedical Informatics, University of Colorado School of Medicine, Aurora, CO 80045, USA
  · Funded by The Gordon and Betty Moore Foundation, GBMF4552; The National Human Genome Research Institute, R01 HG010067; The Eunice Kennedy Shriver National Institute of Child Health and Human Development, R01 HD109765
\end{itemize}

@@

>>>>

\begin{itemize}
\item
  \textbf{Milton Pividori, Ph.D.}
  \includesvg[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0002-3035-4403}{0000-0002-3035-4403}
  · \includesvg[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/miltondp}{miltondp}
  · \includesvg[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/miltondp}{miltondp}
  · \includesvg[width=0.16667in,height=0.16667in]{images/mastodon.svg}
  \href{https://genomic.social/@miltondp}{@miltondp@genomic.social} \\
  Department of Biomedical Informatics, University of Colorado School of Medicine, Aurora, CO 80045, USA; Department of Genetics, Perelman School of Medicine, University of Pennsylvania, Philadelphia, PA 19104, USA
  · Funded by The National Human Genome Research Institute, K99/R00 HG011898; The Alfred P. Sloan Foundation, G-2023-20989; The Eunice Kennedy Shriver National Institute of Child Health and Human Development, R01 HD109765
\item
  \textbf{Casey S. Greene, Ph.D.}
  \textsuperscript{\protect\hyperlink{correspondence}{\Letter}}
  \includesvg[width=0.16667in,height=0.16667in]{images/orcid.svg}
  \href{https://orcid.org/0000-0001-8713-9213}{0000-0001-8713-9213}
  · \includesvg[width=0.16667in,height=0.16667in]{images/github.svg}
  \href{https://github.com/cgreene}{cgreene}
  · \includesvg[width=0.16667in,height=0.16667in]{images/twitter.svg}
  \href{https://twitter.com/GreeneScientist}{GreeneScientist}
  · \includesvg[width=0.16667in,height=0.16667in]{images/mastodon.svg}
  \href{https://genomic.social/@greenescientist}{@greenescientist@genomic.social} \\
  Center for Health AI, University of Colorado School of Medicine, Aurora, CO 80045, USA; Department of Biomedical Informatics, University of Colorado School of Medicine, Aurora, CO 80045, USA
  · Funded by The Gordon and Betty Moore Foundation, GBMF4552; The National Human Genome Research Institute, R01 HG010067; The Eunice Kennedy Shriver National Institute of Child Health and Human Development, R01 HD109765
\end{itemize}

@@

\hypertarget{funding-statement}{%
\subsection{Funding statement}\label{funding-statement}}

This work was supported by:
The National Human Genome Research Institute grant numbers K99/R00 HG011898 and R01 HG010067;
The Eunice Kennedy Shriver National Institute of Child Health and Human Development grant number R01 HD109765;
The Alfred P. Sloan Foundation grant number G-2023-20989;
The Gordon and Betty Moore Foundation grant number GBMF4552.

\hypertarget{competing-interests-statement}{%
\subsection{Competing interests statement}\label{competing-interests-statement}}

TODO: complete

\hypertarget{data-availability-statement}{%
\subsection{Data availability statement}\label{data-availability-statement}}

TODO: complete

\hypertarget{contributorship-statement}{%
\subsection{Contributorship statement}\label{contributorship-statement}}

TODO: complete
